---
output: github_document
---

# qualitycontrol


The goal of qualitycontrol is to set a data quality control framework

## Installation

You can install the qualitycontrol from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("luisgarcez11/qualitycontrol")
```

### Data

The `als_data` dataset will be used to guide you through the package functionality. This data is not real, but based on data retrieved from Amyotrophic Lateral Sclerosis patients.

```{r example, eval = TRUE}
library(qualitycontrol)
als_data
```

### QC mapping

The `als_data_qc_mapping` is an `R list` which contains 3 tables specifying all the tests used for quality control. You can specify your own tests, by creating an excel file and then read it using the function `read_qc_mapping`.

#### Missing
```{r}
als_data_qc_mapping$missing
```

#### Inconsistencies
```{r}
als_data_qc_mapping$inconsistencies
```

#### Out of range values
```{r}
als_data_qc_mapping$range
```


### `qc_data` function

`qc_data` takes as arguments the data to be quality controlled and the QC mapping containing the tests to be applied.

```{r}
qc_data(als_data, als_data_qc_mapping)[,c("subjid","age_at_onset","onset","baseline_date","death_date","finding")]
```

 This will return a table with all the findings. If you want to save it, you can specify the path to be saved in `output_file`.
